Where Do Population III Stars Form?

### 2019-04-02 paper.tex
added rough paragraphs for the comparison, caveat, and conclusion sections. also included rough comparison plot

There are a few caveats to this work that should be noted. Work done by \citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo. In our work, we allow all LW photons to escape the halo. Since we are not accounting for the reduced escape fraction within our halos, we are overestimatng the LW radiation coming from point sources in our simulation. We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results. We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}. Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with redshift. Pop III star formation is delayed by increasing the halo  mass needed to overcome the bulk velocity. Often in the literature, streaming velocities are only studied for a few halos. But \citep{Naoz13} estimates the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be see in Figure \ref{fig:compare_JLW_mass}. These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the halos in our simulation. \citep{Naoz13} mention that at the largest streaming velocity, their simulations don't match expected value due to a small sample size of high mass halos. If we included streaming velocities, the gas would've already fallen into the dark matter potential well when the halo exceeds this characteristic mass. Because of this, streaming velocities would likely not affect our results. Finally, there is the obvious caveat of the unknown Pop III initial mass function (IMF). Like with any work done trying to model Pop III star formation, an IMF must be chosen. Therefore, we have uncertainties coming from the assumed Pop III IMF.

>>>>

There are a few caveats to this work that should be noted. Work done by \citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo. In our work, we allow all LW photons to escape the halo. Since we are not accounting for the reduced escape fraction within our halos, we are overestimatng the LW radiation coming from point sources in our simulation. We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results. We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}. Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with redshift. Pop III star formation is delayed by increasing the halo  mass needed to overcome the bulk velocity. Often in the literature, streaming velocities are only studied for a few halos. But \citet{Naoz13} estimates the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be see in Figure \ref{fig:compare_JLW_mass}. These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the halos in our simulation. \citet{Naoz13} mention that at the largest streaming velocity, their simulations don't match expected value due to a small sample size of high mass halos. If we included streaming velocities, the gas would've already fallen into the dark matter potential well when the halo exceeds this characteristic mass. Because of this, streaming velocities would likely not affect our results. Finally, there is the obvious caveat of the unknown Pop III initial mass function (IMF). Like with any work done trying to model Pop III star formation, an IMF must be chosen. Therefore, we have uncertainties coming from the assumed Pop III IMF.
